Individual Representation: Harm and Utility(?)

### 2021-08-24 paper/paper.Rmd
up
progress
Update paper.Rmd

---
title: Individual Injury and Representational Harms (?)
authors:
  - name: Cory McCartan
    thanks: Footnote stuff
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - standing
bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
---

@@

- introduce partisan symmetry
  - Katz, King, Rosenblatt 2019; Deford et al 2021; Katz, King, Rosenblatt 2021

- Election law side is very indivudalized
  - Standing discussions 
    - Lujan v Defenders of Wildlife (1992)
    - Shaw v. Reno (1993) -- racial gerrymandering
    - Issacharoff and Karlan 1998

- Recent work
  - EGap
  - Partisan Dislocation

- Power of Ensemble Analysis
  - Recent advances allow us to make claims about harm based in counterfactuals that are realistic and statistically useful

>>>>

---
title: Individual Representation: Harm and Utility(?)
authors:
  - name: Cory McCartan
    thanks: Footnote stuff
    department: Department of Statistics
    affiliation: Harvard University
    location: Cambridge, MA
    email: cmccartan@fas.harvard.edu
  - name: Christopher T. Kenny
    department: Department of Government
    affiliation: Harvard University
    location: Cambridge, MA
    email: christopherkenny@fas.harvard.edu
abstract: |
  Enter the text of your abstract here.
keywords:
  - partisan fairness
  - representation
  - redistricting simulation
  - standing
bibliography: references.bib
biblio-style: unsrt
output: 
  rticles::arxiv_article:
    keep_tex: true
---

@@

Understanding fairness in electoral systems has long suffered from a focus on parties over the individuals who vote for them.
There is no doubt that parties are interesting units in electoral discussions.
They offer stability over candidates, information for the under-informed, and shortcuts for understanding preferred vote choices.
Yet, court histories and academic traditions value the harm of the individual over the harm to a transient political body, such as the party.

In this article, we offer an approach to understanding partisan fairness through a lens of individual harm and utility.
This does not supplant existing understandings of partisan fairness, but instead offers an alternative rooted in understanding how the individual potential voters are impacted by districting plans.

Several existing methods of redistricting simulation rely on randomness, such as Random Seed and Grow (Chen and Rodden 2013) or Recombination (Deford et al. 2021).
Moving beyond these hueristic methods, we can use sampling methods that have defined target distributions to ensure that we characterize the space of applicable plans properly.
Methods which operationalize a statistics-based approach include Fifield et al. 2020, McCartan and Imai (2020), and Autrey et al (2020).
Using these methods advance us beyond the critiques of Katz, King, and Roseblatt (2020) by sampling plans using weights within a Gibbs distribution, rather than assuming that uniform sampling weights alone are sufficient.

-   introduce partisan symmetry

    -   Katz, King, Rosenblatt 2019; Deford et al 2021; Katz, King, Rosenblatt 2021

-   Election law side is very indivudalized

    -   Standing discussions

        -   Lujan v Defenders of Wildlife (1992)
        -   Shaw v. Reno (1993) -- racial gerrymandering
        -   Issacharoff and Karlan 1998

-   Recent, related work

    -   EGap
    -   Partisan Dislocation

-   Important to consider benefits and harms to individual voters

-   Power of Ensemble Analysis

    -   Recent advances allow us to make claims about harm based in counterfactuals that are realistic and statistically useful

# Voter Utility in Election Outcomes

1.
